HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex

%     [level 1/.style={sibling distance=7.5em},
%       level 2/.style={sibling distance=5em},

@@

%%  \adjustbox{width=\textwidth,center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

@@

@@

\paragraph{Technical Differences}

+ allows for multi-word and even non-contiguous elements

+ allows to indicate the quality of the predicates ("Actions")

\oa{I would consider adding further examples from the Google Doc. For instnace ``your risk of falling'' -- ``Ihr Risiko'' or
  ``Two {\bf review} authors assessed the studies independently and extracted outcome data'' -- ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf \"uberpr\"ufen}''}

>>>>

%     [ level distance=12mm,
%	   level 1/.style={sibling distance=7.5em,level distance=7mm},
%       level 2/.style={sibling distance=5em,level distance=12mm},

@@

%    % Ondrej removed the width=\textwidth from the options below to keep font
%	% unenlarged:
%  \adjustbox{center,margin=.5em}{\it His old daughter loved tennis, and took daily lessons however good he was}

@@

It is also relatively common in translation that verbal constructions get
nominalized or vice versa. An example from our dataset:
  ``Two {\bf review} authors assessed the studies independently\dots{}'' --
  ``Zwei Autoren bewertete die Studien unabh\"angig zu {\bf
  \"uberpr\"ufen}\dots{}'' (lit. ``Two authors assessed the studies
  independently to be reviewed\dots").\XXX{This is Omri's example, with
  Ondrej's gloss for German. Ondrej is
  not totally sure that the meaning is well preserved.}

Here is \XXX{another} example with a missing linker: the source \equo{However,
this review\dots} was translated as \equo{Diese
Überprüfung\dots} (lit. \equo{This review}). The omission is not by HMEANT at
all.

@@

\paragraph{Annotation of Predicates}

HUME allows to annotate multi-word and even
non-contiguous elements as a single unit. HMEANT, on the other hand, always
required exactly one word to be annotated as the predicate (``Action''), which
is often linguistically inadequate.

Another problem with HMEANT identified by \perscite{bojar:wu:ssst:2012} was the
inability to indicate that the predicate is somewhat mistranslated (e.g.
accidentally negated or in a slightly wrong tense). HMEANT
annotation allows either to mark the source and reference frames as matching
(which implies that the corresponding predicates are correct translations of each
other), or as non-matching (which leads to a zero score for the whole frame) but
nothing in between. In HUME, the verb is still present as a sub-unit of the
frame and has the traffic-lights annotation.

\XXX{Omri: I would consider adding further examples from the Google Doc. For instnace
``your risk of falling'' -- ``Ihr Risiko''.
Ondrej: I don't see any HMEANT problem here, the whole NP 'your risk of falling'
is aligned with 'Ihr Risiko' and HMEANT allows to indicate that the match was
partial, to that's probably what everyone would choose. I've put the other
example higher, but please have a look, I'm not sure if we should keep it there
at all.}
